Defining properties regulating pioneer-factor binding and function

### 2023-02-22 manuscript/manuscript_sections/_06_Figure_Legends.qmd
Add legends for Supp figs 9 and 10

**Extended Data Figure 9: Expression of Zld, Grh, or Twi at supraphysiological levels results in novel binding sites**

-   Western blot showing protein levels for titration experiments

-   Examples of novel binding sites for each factor

-   motif enrichment at novel binding sites

-   Chromatin features at novel binding sites.

**Extended Data Figure 10:**

-   Western blots for determining DBD expression levels

-   IF to confirm nuclear localization of DBDs.

-   Analysis of Zld DBD ChIP only at CAGGTAG sites

-   Examples of any novel DBD binding sites not detected for full-length proteins

-   FL and DBD preference for motifs that are in open vs. closed chromatin: % of closed vs. open motifs bound, motif scores for accessible bound, accessible unbound, inaccessible bound, and inaccessible unbound.

>>>>

**Extended Data Figure 9: Expression of Zld, Grh, or Twi at supraphysiological levels results in chromatin opening at a small number of novel binding sites. a-c,** Immunoblots showing Zld (a), Grh (b) or Twi (c) protein levels when stable cell lines are induced using different concentrations of CuSO~4~. **d-f,** Bar plots showing the percentage of previously defined class I-VI binding sites that are bound by Zld (d), Grh (e), or Twi (f) when expressed at varying concentrations. **g-i,** Bar plots showing the percentage of previously defined class I-VI binding sites that overlap an ATAC-seq peak when Zld (g), Grh (h), or Twi (i) are expressed at varying concentrations.

**Extended Data Figure 10: Expression of Zld and Grh DNA-binding domains at protein levels comparable to the full-length proteins. a-b,** Immunoblots showing titration of protein levels for Zld (a) or Grh (b) DNA-binding domains to match expression of the full-length proteins. DNA-binding domain protein levels are shown at a range of CuSO~4~ concentrations and compared to an equivalent number of cells expressing full-length Zld or Grh at approximately physiological levels. **c,** Metaplots showing the average ChIP-seq signal for full-length Zld or the DNA-binding domain alone at the subset of previously identified class I, II or III binding sites that contain a canonical Zelda CAGGTAG motif.
